Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Small changes

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors. For each of the actuators and sensors, the color indicates the principal direction}
  \label{fig:avis:withAxes}
\end{figure}

@@

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.

>>>>

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

@@

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.
